Improving Dynamic Kidney Exchange

### 2018-02-11 paper.tex
Added algorithms

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,caption,color,setspace,sectsty,comment,footmisc,pdflscape,subfigure,array,hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{natbib}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[font=footnotesize]{caption}

@@

@@

\paragraph{Main idea} We propose a new dynamic kidney matching algorithm that takes as input a pool of patient-donor pairs and computes, for each cycle that is currently available for matching, a probability that it should be chosen to be cleared today, as well as another probability indicating whether we should not match any more cycles. In order to get these probabilities, our algorithm first produces a prior distribution estimated by observing past choices made by an infeasible optimal algorithm, and then updates these priors with simulations.

@@

The distribution of blood types in the US population is roughly O:48\%, A:36\%, B:11\%, AB:4\%. If we initially independently draw two people from this distribution and they form, say, an (A,B) pair (which happens with probability $0.36 \cdot 0.12 \approx 0.0432$), then we allow them to the pool immediately, since their B-donor is blood-type incompatible with their A-patient. However, if they happen to form an (A,O) pair (with probability $0.36 \cdot 0.48 \approx 0.172$), then they should only enter the pool if the donor and patient are tissue-type incompatible, otherwise the O donor would immediately donate their kidney to the patient and they would not need to enter the exchange pool at all. So we assume the probability of a positive crossmatch is $p_c = 0.11$ as in \cite{zenios2001primum}, then the probability that two people form an (A,O) and enter the pool becomes in fact $0.36 \cdot 0.48  \cdot 0.11 \approx 0.019$. By computing the probabilities of each pair in this manner and then normalizing so that they add up to one, we arrive at the numbers displayed on Table \ref{tab:abo_blood_type}.

>>>>

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,caption,color,setspace,sectsty,comment,footmisc,pdflscape,subfigure,array,hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{natbib}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[font=footnotesize]{caption}
\usepackage{lineno}

@@

\linenumbers

@@

\paragraph{Main idea} We study new dynamic kidney matching algorithm that takes as input a pool of patient-donor pairs and computes, for each cycle that is currently available for matching, a probability that it should be chosen to be cleared today, as well as another probability indicating whether we should not match any more cycles. In order to get these probabilities, our algorithm first produces a prior distribution estimated by observing past choices made by an infeasible optimal algorithm, and then updates these priors with simulations.

@@

The distribution of blood types in the US population is roughly O:48\%, A:36\%, B:11\%, AB:4\%. If we initially independently draw two people from this distribution and they form, say, an (A,B) pair (which happens with probability $0.36 \cdot 0.12 \approx 0.0432$), then we allow them to the pool immediately, since their B-donor is blood-type incompatible with their A-patient. However, if they happen to form an (A,O) pair (with probability $0.36 \cdot 0.48 \approx 0.172$), then they should only enter the pool if the donor and patient are tissue-type incompatible, otherwise the O donor would immediately donate their kidney to the patient and they would not need to enter the exchange pool at all. So we assume the probability of a positive crossmatch is $p_c = 0.11$ as in \cite{zenios2001primum}, then the probability that two people form an (A,O) and enter the pool becomes in fact proportional to $0.36 \cdot 0.48  \cdot 0.11 \approx 0.019$. By computing the probabilities of each pair in this manner and then normalizing so that they add up to one, we arrive at the numbers displayed on Table \ref{tab:abo_blood_type}.
